Your Paper Title

### 2025-05-13 Master Thesis/thesis.tex
New

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\onehalfspacing

@@

In D spacetime dimensions, the little group for massive particles is $SO(D-1)$. For massless
particles the little group is the the group of Euclidean symmetries in (D−2) dimensions, which
is $SO(D-2)$.In this article, we mainly discuss massless particles scattering in 4 dimension spacetime, so the little group is $SO(2)\backsimeq U(1)$.

@@

First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
\begin{itemize}
    \item $\sum_{i=1}^{n}r_i^\mu=0$,
    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
    \item $p_i\cdot r_i=0$ for each i(no sum).
\end{itemize}
These vectors $r_i$ are used to define n shifted momentum
\begin{equation}
    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
\end{equation}
Note that, by imposing these constraints,
\begin{itemize}
    \item Momentum conservation holds for the shifted momentum:
\end{itemize}

\bibliographystyle{unsrt}
\bibliography{reference.bib}

>>>>

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{float}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\onehalfspacing

@@

In D spacetime dimensions, the little group for massive particles is $SO(D-1)$. For massless
particles the little group is the the group of Euclidean symmetries in (D - 2) dimensions, which
is $SO(D-2)$.In this article, we mainly discuss massless particles scattering in 4 dimension spacetime, so the little group is $SO(2)\backsimeq U(1)$.

@@

First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
\begin{itemize}
    \item $\sum_{i=1}^{n}r_i^\mu=0$,
    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
    \item $p_i\cdot r_i=0$ for each i(no sum).
\end{itemize}
These vectors $r_i$ are used to define n shifted momentum
\begin{equation}
    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
\end{equation}
Note that, by imposing these constraints,
\begin{itemize}
    \item Momentum conservation holds for the shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
    \item We have $\hat{p}_i^2=0$, so each shifted momentum still keep on-shell
    \item For a non-trival \footnote{non-trival here means at least two and no more than n-2 such that $P_I^2\neq 0$} subset of momentum $\{p_i\}_{i\in I}$,
    define $P_i^\mu=\sum_{i\in I}p_i^\mu$. Then $\hat{P}_I^2$ is \textbf{linear} in z:
    \begin{equation}
        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I)
    \end{equation}
    beacuse the $z^2$ term vanishes. We can write 
    \begin{equation}
        \hat{P}_I^2=-\frac{P_I^2}{z_I}(z-z_I)\quad \text\quad {with} z_I=\frac{P_I^2}{2P_I\cdot k}
        \label{2.63}
    \end{equation}
\end{itemize}
If we consider the original amplitude $A_n$ in terms of the shifted momentum $\hat{p}_i^\mu$ instead of original momentum. Then the amplitude can be seen as 
a holomorphic function of z. Actually, if we set $z=0$, we can obtain the origin ampltide $A_n=\hat{A}_n(z=0)$.

In this paper, we only focus on the tree-level scatterung amplitudes, in which case the analytic structure becomes quite simple. The tree amplitudes does not have any branch cuts -- there are no 
logs, no square roots, etc.. The tree-level amplitude is a rational function of Lorentz invariant kinematic quantities, like the contraction between momentum or momentum and polarization vector. 
Therefore, the analytic structure can be completely captured by its single poles in the complex z plane. To see that all of the poles are single, we just need to notice 
that we can only ontain poles from propagators. But we have seen that all of the poles can be dertermined by  \eqref{2.63}. 
So $1/\hat{P}_I^2$ gives a single pole at $z_I$, and for generic momentum, $P_I^2\neq 0$(propagator is off-shell) so $z_I\neq 0$. Hence, 
$\hat{A}_n(z)$ only has single poles away from the orignal poine $z=0$.\footnote{Here we need to impose locality to ensure all of the poles can be determined by the propagators.}

Then let us turn to define a new holomorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane. We can pick a contour surrounding the original point 
$z=0$ which is a single pole of this function. The residue of this single pole can be easily computed
\begin{equation}
    \mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(z=0)=A_n,
\end{equation}
It is just the unshifted amplitude what we want to compute at the begining.

Also, we can choose another countour surrounding all single poles, then Cauchy's theorem just tell us 
\begin{equation}
    A_n = - \sum_{z_I} \mathrm{Res}_{z=z_I} \frac{\hat{A}_n(z)}{z}  + B_n\,,
\end{equation}
where the $B_n$ is the residue at $z=\infty$ infinity, called bounday term. By taking $z\rightarrow 1/\omega$, it is easy to notice that
$B_n$ is the $O(z^0)$ term in the $z\rightarrow \infty$ expansion of $A_n$.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{Cau.png} % 调整为所需大小
    \caption{Cauchy Theorem}
\end{figure}

Now, at the position of $z_I$ pole, the propagator $1/\hat{P}_I^2$ gose on-shell. The unitarity has a tight relation with I poles in the S-matrix with on-shell intermediate
states.
\begin{equation}
    G_n(p_1, \ldots, p_n) = (2\pi)^4 \, \delta^4\left(\sum p\right) 
\frac{i}{p_\Psi^2 - m_\Psi^2 + i\varepsilon} 
\mathcal{M}_\Psi^{1,r} \, \mathcal{M}_\Psi^{r+1,n\dagger} + \text{extra}
\end{equation}
where “extra” refers to anything else that contributes. This equation says that Green’s
functions always have poles when on-shell intermediate particles can be produced.

Then, in the on-shell limit, the shifted amplitude \textit{factorizes} into two on-shell parts
\begin{equation}
     \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
\end{equation}

This makes it easy to compute the residue at $z=z_I$
\begin{equation}
    -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=-(z-z_I)\frac{z_I}{z(z-z_I)}|_{z=z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
\end{equation}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{recrel1.pdf} % 调整为所需大小
    \caption{factorization}
\end{figure}

Note that, as opposed to Feynman diagrams for which the intermediate propagator does not equal to 0, here the intertal line $\hat{P}_I^2$ of Figure 2 does equal to 0.
And the blobs which refer to subamplitudes are \tif{on-shell amplitudes}. In the diagrammatic representation Figure 2, the internal line is assigned the usual scalar propagator 
$1/P_I^2$, evaluated using unshifted momenta. Since each subamplitude involves fewer than 
n external particles, all the residues at finite z can be expressed entirely in terms of lower-point on-shell amplitudes. 
This fundamental idea underlies the construction of the recursion relations.

The contribution $B_n$ does affect a lot, and it has no similar general expression in trems of lower-point amplitudes. Although in some cases, the boundary term
$B_n$ can be computed, but there is not a general method to compute it. Thus, in most applications, we always assumes, or better, prove that $B_n=0$. This is often modified
by demonstrating stronger statement that 
\begin{equation}
    \hat{A}_n(z) \to 0 ~~~~ \text{for} ~~~~ z \to \infty. 
    \label{2.69}
\end{equation}
If \eqref{2.69} holds, we state the shift is \tif{valid}.

For a valid shift, the n-point amplitudes can be recursively computed interms of lower-point amplitude
\begin{equation}
     A_n ~= \sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
    \,\frac{1}{P_I^2}\,
    \hat{A}_\text{R}(z_I)
       ~~=
   \sum_{\text{diagrams}~I}
   \raisebox{-5.5mm}{\includegraphics[height=1.4cm]{recrel1}}
   \,.
\end{equation}
where I means all possible factorization channels. We did not use any $D=4$ spacetime property, so this recursion relation can be 
utilized to general D dimension spacetime.

\subsubsection{BCFW recursion relation}
In the last section, we introduce the recursion relation with all momentum shifted. But actually, some of the shift vectors $r_i^\mu$ can be choose to 0.
The BCFW shift is a kind of special shift for which only two momentum are shifted, called i and j. In D=4 spacetime diension, the shift is implemented 
\begin{equation}
    \hat{p}_i(z)=p_i-zq,\qquad \hat{p}_j(z)=p_j+zq
    \label{2.71}
\end{equation}
so momentum conservation is kept and the hold for on-shell condition require ot impose
\begin{equation}
    q^2=q\cdot p_i=q\cdot p_j=0 \, .
\end{equation}
This shift can be implemented in terms of spinor-helicity variable as
\begin{equation}
    |\hat{i}] = |i] - z\,|j]\,,   
  ~~~~~~
  |\hat{j}] = |j]\,,   
  ~~~~~~
  |\hat{i}\rangle = |i\rangle\,,
  ~~~~~~
  |\hat{j}\rangle = |j\rangle + z |i\rangle \,.
\end{equation}
No other spinors are shifted, this kind of shift are called $[i,j\rangle$ shift(it is worth to mention that $[i,j\rangle$ shift 
is completely different with $[j,i\rangle$ shift). In the literature, the BCFW
deformation is usually written in the above spinor form. However, the momentum form \eqref{2.71} provides
another perspective.

The BCFW recursion relation takes the form
\begin{equation}
     A_n ~= \sum_{\text{diagrams}~I} \hat{A}_\text{L}(z_I) 
    \,\frac{1}{P_I^2}\,
    \hat{A}_\text{R}(z_I)
       ~~=
   \sum_{\text{diagrams}~I}
   \raisebox{-5.8mm}{\includegraphics[height=1.4cm]{recrel.2.png}}
   \,.
\end{equation}

Beforing going into the apllication of BCFW, let us first consider the large-z behavior. 
In pure Yang-Mills case, it has been proved that the color-ordered gluon tree-level amplitudes behave like the following manner\cite{Arkani-Hamed:2001kyx}
$$ 
\begin{array}{cccccc}
   [i,j\rangle & [-,-\rangle & [-,+\rangle & [+,+\rangle & [+,-\rangle &
   \\[2mm]
   \hat{A}_n(z) \sim 
   &  \frac{1}{z} &  \frac{1}{z} &  \frac{1}{z} & z^3
   \end{array}
$$
If i,j are not adjacent, one obtains an extra $1/z$ in each case. Thus any one of shifts $,[-,-\rangle,[-,+\rangle,[+,+\rangle$ are valid
but $[+,-\rangle$ is not valid. This is a quite non-trival result.

\newpage
\bibliographystyle{unsrt}
\bibliography{reference.bib}
